%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../doc"
%%% coding: utf-8
%%% End:
% !TEX TS-program = pdflatexmk
% !TEX encoding = UTF-8 Unicode
% !TEX root = ../doc.tex

This section consists of the state of the art and the definition of the project. In the state of the art, the existing software prototype for this project and the approaches used for it are briefly explained. In the definition of project, the tasks and aims of the project are described, based on the definition provided by the supervisor.

\section{Initial position} \label{Initial position}
Toggl Track \cite{toggl_track_url} is an online application frequently used for time planning and tracking for projects or tasks. However, it does not provide the flexibility demanded by teachers and students in order to properly plan, track and compare their time efforts \cite{bachelorarbeit_Egger_Verstappen_page2}. In the bachelor thesis \cite{bachelorarbeit_Egger_Verstappen_page1} on which this project is based, a technological prototype of an academic time planning software (Academic Time Planner, ATP) has been developed. The ATP is designed for complementary use with Toggl Track. The prototype has been realized as a .NET Blazor application fetching time data collected on Toggl Track via the Toggl Track API. Moreover, a concept for mapping Toggl Track time data to ATP-specific time data as well as mockups for the graphical user interface of the ATP have been evaluated.

\section{Definition of project} \label{Definition}
Students and teachers have to organise their time for different tasks. The ATP is intended to support them in this matter, allowing for a semester-oriented time planning and helping to keep to the timing plans. To achieve this, the difference between planed time and used time should always be visible. The time tracked is read via an API from Toggl Track (see chapter \ref{Initial position}). The goal of this project is to create a prototype based on the technological prototype already created and to realize the mapping concept, focussing on good and simple usability.

The prototype should be able to run locally and display an overview over the current difference between planed time and used time. To allow for proper handling of time planning data, it should be grouped into plan projects. A plan project contains all time planning data for a certain project (e. g. a semester module). Furthermore, it should include the state of the application as to whether the data fetched from Toggl Track is up-to-date and if there are any inconsistencies between plan projects and Toggle Track projects. In addition to that, the import and export of planning data as well as the creation of plan projects via the application GUI should be made possible.

The following chapters describe the realization of the project. In chapter 2, the fundamentals of the realization are explained. In chapter 3, the methods are described, and in chapter 4 the results. In chapter 5, the results from chapter 4 are discussed and further steps are suggested.
 


